---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# modulR

<!-- badges: start -->
<!-- badges: end -->

This R package helps do modular arithmetic operations. In particular, it can
give arithmetic (multiplication) tables in modular space.

It is a demo package meant to show some strategies for creating packages and
illustrates some basic S3 classes in R. It is not meant for production use. A
better package for doing modular arithmetic in R would be the
[gmp](https://cran.r-project.org/package=gmp) package (or base R!).

## Installation

``` r
remotes::install_github("pegeler/modulR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(modulR)

# Initialize
z11 <- m_arithmetic(11)
z11

# What is 13 in Z_11?
z11$identity(13)

# Multiplication table in Z_11
z11$tables$mul
```

